Objective-first optimization for nanophotonics

### 2012-05-31 presentations/meta_book/wave_eq.tex
Small commit.

\section{The electromagnetic wave equation}
\subsection{Physics formulation}
Let's talk about the electromagnetic wave equation from a physics standpoint.
Let's start from Maxwell's equations without currents.
\BA \curl E = - \mu_0 \frac{\partial H}{\partial t} \\
    \curl H = J + \epsilon \frac{\partial E}{\partial t} \EA

>>>>

\section{The electromagnetic wave equation}

\subsection{Physics formulation}
We will start by reviewing 
    the fundamental physical equation governing nanophotonics, 
    the electromagnetic wave equation.

We first derive the wave equation by starting with Maxwell's equations:

\BA \curl E = - \mu_0 \frac{\partial H}{\partial t} \\
    \curl H = J + \epsilon \frac{\partial E}{\partial t} \EA
